### 2016-10-01 results.tex
cheers

\subsection{Domain-Separated PRF-Hash}
\jnote{Give English-language description of scheme before turning to
analysis of correctness.}

>>>>

\subsection{Domain-Separated PRF-Hash}
Next we consider a natural, secret-key variant of the classic Bloom
filter.  Here the (private) hash functions are instantiated via
$H(j,x)=F_K(\langle j,x\rangle)$, using domain-separation to turn a
PRF (with one secret key) into, effectively, multiple functions that
are computationally indistinguishable from random.  We call this the
domain-separated PRF-hash data structure.
